Validation of Visual Statistical Inference, Applied to Linear Models

### 2012-07-20 paper_jasa.tex
discussion on chapters

The paper is organized as follows. Section \ref{sec:visual_test} defines terms as used in visual inference, and describes how to estimate the important quantities from experimental data. The effect of the lineup size and number of observers on the power of the test is discussed in Section \ref{sec:size}. Section \ref{sec:regression} focuses on the application of  visual inference to linear models.  Section \ref{sec:simulation} describes the results of the three simulation experiments conducted to compare the power of the lineup protocol with the equivalent conventional test and an analysis of the resulting data. The last section describes the next steps in this research.

@@

\section{Results}

@@

\begin{figure*}[hbtp]
   \centering
      \includegraphics[width=0.95\textwidth]{p_val_log_counts-a.pdf}
       \includegraphics[width=0.95\textwidth]{p_val_log_counts-b.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the 60 individual lineups for experiment 1. Red indicates the plot with the lowest $p$-value, and 
       blue indicates the actual data plot, when it is different from that with the lowest $p$-value. 
       The columns of both top and bottom panel are ordered according to effect size, rows within panels show replicates for each parameter combination.
       }
       \label{fig:P-val_log}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.75\textwidth]{p_val_log_counts2-a.pdf}       
       \includegraphics[width=0.75\textwidth]{p_val_log_counts2-b.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the 70 individual lineups for experiment 2. Red indicates the plot with the lowest $p$-value, and blue indicates the actual data plot, when it is different from that with the lowest $p$-value. 
Columns are ordered according to effect size, with rows showing replicates of the same parameter combination on top of each other.
       Empty cells indicate combination of parameters with fewer than five replicates. 
       Highest counts tend to be the plot in the lineup having the lowest $p$-value, even more so than for experiment 1.
       }
       \label{fig:P-val_log2}
\end{figure*}

>>>>

The paper is organized as follows. Section \ref{sec:visual_test} defines terms as used in visual inference, and describes how to estimate the important quantities from experimental data. The effect of the lineup size and number of observers on the power of the test is discussed in Section \ref{sec:size}. Section \ref{sec:regression} focuses on the application of  visual inference to linear models.  \blue{Section \ref{sec:simulation} describes the three simulation experiments conducted to compare the power of the lineup protocol with the equivalent conventional test and  Section \ref{sec:results} presents the results of the experiments with analysis of the resulting data.} The last section describes the next steps in this research.

@@

\section{Results} \label{sec:results}

@@

\begin{figure*}[hbtp]
   \centering
      \includegraphics[width=0.95\textwidth]{p_val_log_counts-a.pdf}
       \includegraphics[width=0.95\textwidth]{p_val_log_counts-b.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the 60 individual lineups for experiment 1. Red indicates the plot with the lowest $p$-value, and blue indicates the actual data plot, when it is different from that with the lowest $p$-value. The columns of both top and bottom panel are ordered according to effect size, rows within panels show replicates for each parameter combination.}
       \label{fig:P-val_log}
\end{figure*}

\begin{figure*}[hbtp]
   \centering
       \includegraphics[width=0.95\textwidth]{p_val_log_counts2-a.pdf}       
       \includegraphics[width=0.95\textwidth]{p_val_log_counts2-b.pdf}
       \caption{Relative frequency of plot picks compared to other plots in the lineup plotted against the $p$-value (on log$_{10}$ scale) of each plot for all of the 70 individual lineups for experiment 2. Red indicates the plot with the lowest $p$-value, and blue indicates the actual data plot, when it is different from that with the lowest $p$-value. 
Columns are ordered according to effect size, with rows showing replicates of the same parameter combination on top of each other.
       Empty cells indicate combination of parameters with fewer than five replicates. 
       Highest counts tend to be the plot in the lineup having the lowest $p$-value, even more so than for experiment 1.
       }
       \label{fig:P-val_log2}
\end{figure*}
